Index measures for oak decline severity using phenotypic descriptors

### 2019-11-12 manuscript/manuscript.Rmd

---
title: "Index measures for oak decline severity using phenotypic descriptors"
output: 
  bookdown::pdf_document2:
   toc: false
   number_sections: false
keep_tex: yes
---

>>>>

---
title: "Index measures for oak decline severity using phenotypic descriptors"
output: 
  bookdown::pdf_document2:
   toc: false
   number_sections: false
   keep_tex: no
---

### 2019-11-12 manuscript/supplementary.Rmd
tex no longer kept

---
output: pdf_document
---

@@

>>>>

---
output: 
  pdf_document:
    keep_tex: no
---

## Supplementary information

@@

```{r descriptor_adjustment_factors}
loadd(site_correction_factors)

site_correction_factors %>%
  kable(caption = 'Descriptor correction factors at each site')
```

```{r PDInumeric,fig.height=8}
loadd(descriptor_scatter_plots)

descriptor_scatter_plots$PDI_numeric
```

```{r PDIfactor,fig.height=8}
descriptor_scatter_plots$PDI_factor
```

```{r DAInumeric,fig.height=8}
descriptor_scatter_plots$DAI_numeric
```

```{r DAIfactor,fig.height=8}
descriptor_scatter_plots$DAI_factor
```
